\nofiles
\documentclass{article}
\usepackage{resume}
\usepackage{palatino}
\usepackage{geometry}
\usepackage{multicol}
\begin{document}
\name{Elias Ross}
\address{
1025 NE 73RD Street - Seattle WA 98115 - USA - 425-466-8702 \\
http://www.noderunner.net/\%7Egenman/ - genman@noderunner.net }

% \setlength{\parindent}{0pt}
% \setlength{\leftskip}{0pt}
% \setlength{\parskip}{4pt}

\subsection{Summary}
Architect or technical-lead developer with over fifteen years of experience
developing distributed enterprise services, database and personal computer
applications, development tools, open source solutions, and technical designs.
Highly capable, self-motivated, team player versed in Java and C++, in both
technology integration. Able to speak, read, and write Japanese.

\subsection{Employment}

\employer{Apple} \location{Cupertino, California}
\dates{Production Operations Software Architect, December 2010--Present}

Designed, developed, and deployed the monitoring solution for iAd. iAd
is Apple's ad serving network comprised of thousands of hosts. I was
in charge for providing monitoring for all systems, applications and
third-party services such as Tomcat/JBoss, Oracle, Hadoop, MySQL, MongoDB,
Redis, Memcache, NetScaler, etc. I worked with all teams within iAd to
develop a complete monitoring system. A team of contractors onshore and
offshore support this system and work is ongoing.

I developed the initial monitoring platform using Nagios and Puppet,
and eventually it evolved into a highly scalable and easier to manage
system using RedHat's RHQ platform. RHQ is built on top of JBoss EAP
and uses Cassandra and Oracle Database. The system works across multiple
data centers. On top of RHQ, I developed a custom framework for providing
easy-to-build dashboards for all systems, including business intelligence
and reporting.

I also provided day-to-day assistance to deployment and operations team
members for working with git, Puppet, and packaging tools such as RPM.

I worked closely with RedHat, providing patches and fixes through the
Apple open source process. I am a recognized and prolific contributor
to the RHQ product.

In addition, I worked on designing and developing a Passbook notification
and update solution for iAd designed for supporting millions of devices,
using clustered JMS and Cassandra. I was first to adopt CDI (JEE)
technology and wrote extensions for other team members to expose KPIs
through Java annotations for monitoring purposes.

\employer{Telecommunication Systems and Location Logic, LLC} \location{Seattle, Washington}
\dates{Principal Computer Systems Developer, February 2009-December 2010}

Key developer and support person for entire Location Positioning System
(LPS) for Verizon Wireless; once the responsibility of a large developer
team. This system processed millions of mobile station transactions a
day without fault.

Developed a prototype GLA ("Global Location Agent") solution for Huawei,
a network technology reseller, in under six weeks. Worked with the
customer in Shenzhen China to test our solution on site.

\employer{Autodesk} \location{San Rafael, California}
\dates{Principal Software Engineer, September 2006-February 2009}

Solutions lead for the Verizon Windows Mobile project. Primary developer
for various new server-side components for Verizon billing systems
integration and service authorization for support of advanced devices.

Introduced to team new technologies for creating better products and
productivity. Technologies included JPA/Hibernate, Maven, JMX, and
distributed network caching.

Wrote a performance test harness for the "user-plane mobile positioning
client", or "UP-MPC" component, a server component used at Verizon,
Sprint, and Alltel.

Member and committer for the Apache Software Foundation.

\employer{Verisign (acquired as m-Qube)} \location{Boston, Massachusetts}
\dates{Software Architect, 2002--2006}
Developed a distributed premium messaging billing platform for all major U.S.
and many Canadian carriers. Sole author of critical messaging delivery
components for m-Qube, including SMS, IM, SMTP. Helped take the company from
20 people to over 200.

Designed, built, maintained an SMS/SMPP messaging server called "SMS
Gateway", which delivered \$85 million in premium messaging for 2005.  Created
a custom language to support SMPP routing and connectivity for over 100
connected customers.  System was capable of 3000 standard-rate message
deliveries a second.  Also, designed a billing server which can process and
deliver 200-300 billing or subscription messages per second.

Developed a "dialog XML" language (similar to voice XML) and plug-in
system for handling stateful conversations for SMS and other messaging services.

Recognized contributor to the JBoss project, specifically features for
the JBoss MQ (messaging) and JBoss Cache products, such as scheduled and
delayed message delivery which are now standard JMS features.

\employer{Openwave} \location{Bellevue, Washington}

\dates{Software Developer, 1999--2002}
Responsible for creating components to support enterprise-level services
for determining mobile handset presence and location. Responsible for own
unit-testing, end-to-end testing, technical requirements and design
documents.

Used and leveraged existing components to build an instant messaging
application supporting mobile presence. Used mobile protocols and network
simulators for testing on SS7 networks.  Used UML and the Unified Process.

% \begin{items}
% \item Assisted developers in two teams simultaneously; often reassigned
% to support tasks that were behind schedule.  Mentored UI team in
% UNIX, PHP, JSP, and Java.
% \item Completed two patent applications on document compression (both awarded
% in 2005) and received recognition for three other invention submissions.
% \item Created an XML pull-parser and XML-RPC library, to support streamed
% XML document delivery.  See http://e-xml.sf.net
% \end{items}

\employer{Bellevue Community College} \location{Kirkland, Washington}
\dates{Instructor, 2001--2002}
Computer instruction, teaching a class on UNIX. Responsible for creation
of course materials and content.

\employer{Catdaddy Games} \location{Bellevue, Washington}
\dates{Software Developer, 1998--2000}
Responsible for programming and helping deliver various games and
building a 3D game engine.  Helped complete the game ``Full Strength
Challenge'' as one of two developers.

Sole and lead developer for UI, network components, sound, input,
and 3D model export utilities.

Ported Windows network match server to Linux.

Designed and implemented prototype 3D vehicle game.

% \employer{Berlitz} \location{Sendai, Japan}
% \dates{Teacher, 1998}
% Taught private English lessons to business clients.  Learned the Berlitz
% language teaching approach.

% \employer{Starwave (Presently Go.com)} \location{Bellevue, Washington}
% \dates{Intern, 1996--1997}
% Worked with the online commerce division to develop a database system for
% commerce transactions. Later transferred to work with online fantasy sports
% games (pre-Servlet, but Java-based). Sole author of utility software for
% scheduling services, live systems monitoring, bug-tracking, etc.  Learned Java,
% Perl, ASP, SQL, etc.

% \employer{Steel Silhouettes} \location{Seattle, Washington}
% \dates{Computer Consultant, 1994--1997 }
% HTML authoring, custom software for industrial machine, systems
% troubleshooting. \\ Refer to www.\-steelsilhouettes.\-com

% \employer{Self---DBA Cybersoft} \location{Seattle, Washington}
% \dates{Computer Consultant, 1993--1997 }
% Installation of consumer hardware, answered software package questions.

% \employer{Garfield High School} \location{Seattle, Washington} Assisted
% \dates{Computer Consultant, 1993--1995 }
% installation of first Internet service in Seattle Public Schools, on Windows
% NT.  Wrote HTML pages, performed system maintenance, etc.

\subsection{Education}

\employer{University of Washington}
\location{Seattle, Washington}
\dates{1995--1999}
Awarded Bachelor of Science degree.  Major in applied computational math science.

\employer{Tohoku University}
\location{Sendai, Japan}
\dates{1997--1998 }
Exchange student in Japan in the engineering school. Part-time
research in Japanese character recognition, but mostly focused on
language skills.

\newpage
\subsection{Technologies}

\begin{items}
\item[Java] 15 years. JEE including JPA, CDI; Maven/Gradle.
\item[Puppet] 4 years, Ruby templates, large deployments and config management.
\item[C/C++] 4 years. Solaris cc, gcc, VC++, STL, POSIX.
\item[Perl] 4 years experience.
\item[SQL] 4 years, Oracle, MySQL, SQL Server, stored procedures.
\item[UNIX] 15+ years. Linux (OEL/RHEL 5/6), Solaris, BSD variants.
\item[JavaScript] 2+ years, mostly Rhino scripting and some UI.
\item[Python] 1 year experience.
\item[Cassandra] 1 year, deployment and schema design.
\item[Hadoop] 3 years, deployment, monitoring; Hive, Oozie, Flume.
\item[Ver Control] git, Subversion, Perforce, CVS, Clearquest, VSS.
\item[Networks] 4 years. TCP/IP, HTTP, HTTPS, SMPPv3, UDP.
\item[Shells] 6 years. Bourne, BASH.
\item[Others] Hibernate, Windows, XML, OOP, UML, LDAP, make, ant, Pascal,
Scheme, Ruby, ASP, DirectX, 3D Max, Assembler and compiler design.
\end{items}

\subsection*{Activities and Interests}
\begin{items}
\item Cooking
\item Sea kayaking
\item Road cycling and touring
\item Japanese culture and language, volunteering at anime conventions
\item Hiking and mountaineering
\item Backcountry skiing
\item Free Software
\end{items}

% \sectiontitle{Operating Systems, Hardware}

% UNIX (Solaris, Unixware, Linux, etc.), Windows 2000/NT3.51/4.0, Macintosh
% System 7.  Hardware installation.  Ethernet networking.  Use of hardware
% such as serial switches, industrial RS-232 devices and cutting machines, etc.

% \sectiontitle{Development Related Software}

% Oracle 8/7, Visio, Microsoft SQL Server 6.5, 3D Studio MAX 2.5, MS IIS
% (Web Server), MS Developer's Studio/Source Safe, bug tracking tools,
% LaTeX, Photopaint, CorelDraw, CASMate (Custom CAD design tool),
% Microsoft Office, Quickbooks, Vi, Vim.

% \sectiontitle{Independent Software Projects---historical}

% \begin{itemize}
% \item[`89 ``Duelbots''] Two-player modem strategy game on the
% Commodore 64.  Published Online.  Co-authored.
% \item[`91 ``Duelbots IBM''] Rewrite of Duelbots on the IBM PC. Limited
% computer.  AI. Co-authored.
% \item[`93-95 ``Stellar Conquest''] Text-based multi-user BBS
% game.  Customizable flat-file database design.  Co-authored.
% \item[`93 ``Warlords II Editor'']  A GUI editor, for the
% PC/DOS strategy game, Warlords II.
% \item[`95 ``AddPauses'']  Used in adding machine pauses to ``G-code'',
% the language to control a mechanized cutting table.
% \item[`98 Pattern Recognition] Japanese Character Recognition.  Wrote
% program to segment Japanese addresses and recognize them, used statistical
% pattern recognition.
% \end{itemize}

% \subsection*{References}
% Names and contact information will be provided upon request.

\end{document}
